---
title: "CSN_lab5"
output: html_document
---

```{r}
library(igraph)
library(igraphdata)
library(future)

data("foodwebs")
foodweb_net <- as.undirected(foodwebs[[9]], mode = "collapse")
print("foodweb_net")
gsize(foodweb_net)
gorder(foodweb_net)

data("macaque")
macaque_net <- as.undirected(macaque, mode = "collapse")
print("macaque_net")
gsize(macaque_net)
gorder(macaque_net)

data("enron")
enron_net <- enron
print("enron_net")
gsize(enron_net)
gorder(enron_net)
```


Algorithms to try:

• *edge.betweenness.community* [Newman and Girvan, 2004]
• *fastgreedy.community* [Clauset et al., 2004]: modularity greedy opti-
mization method.
• *label.propagation.community* [Raghavan et al., 2007]: This is a fast, nearly linear time algorithm for detecting community structure in net- works. It works by labeling the vertices with unique labels and then updating the labels by majority voting in the neighborhood of the vertex.
• *leading.eigenvector.community* [Newman, 2006]
• *multilevel.community* [Blondel et al., 2008]: This is a multi-level modularity optimization algorithm (the Louvain method).
• *optimal.community* [Brandes et al., 2008]: Works by maximizing the mod- ularity measure over all possible partitions.
• *spinglass.community* [Reichardt and Bornholdt, 2006]: tries to find com- munities in graphs via a spin-glass model and simulated annealing.
• *walktrap.community* [Pons and Latapy, 2005]: tries to find densely con- nected subgraphs (communities) in a graph via random walks. The idea is that short random walks tend to stay in the same community.
• *infomap.community* [Rosvall and Bergstrom, 2008]: Find community struc- ture that minimizes the expected description length of a random walker tra jectory.


```{r}
future::plan(multicore=3)
communities <- edge.betweenness.community (foodweb_net, directed = FALSE,
    edge.betweenness = TRUE, merges = TRUE, bridges = TRUE)
```



# measures

```{r}
#TPR
communities <- cluster_infomap(foodweb_net)
modularity(communities)

get_TPR(foodweb_net, communities)
```




```{r}

```




