---
title: "CSN_lab5"
output: html_document
---

```{r}
library(igraph)
library(igraphdata)
library(ggplot2)
library(reshape)
library(viridis)
library(dplyr)
source("lab5_script.R")

`%+=%` = function(e1,e2) eval.parent(substitute(e1 <- e1 + e2))

```


Algorithms to try:

• *edge.betweenness.community* [Newman and Girvan, 2004]
• *fastgreedy.community* [Clauset et al., 2004]: modularity greedy optimization method.
• *label.propagation.community* [Raghavan et al., 2007]: This is a fast, nearly linear time algorithm for detecting community structure in net- works. It works by labeling the vertices with unique labels and then updating the labels by majority voting in the neighborhood of the vertex.
• *leading.eigenvector.community* [Newman, 2006]
• *multilevel.community* [Blondel et al., 2008]: This is a multi-level modularity optimization algorithm (the Louvain method).
• *optimal.community* [Brandes et al., 2008]: Works by maximizing the modularity measure over all possible partitions.
• *spinglass.community* [Reichardt and Bornholdt, 2006]: tries to find communities in graphs via a spin-glass model and simulated annealing.
• *walktrap.community* [Pons and Latapy, 2005]: tries to find densely connected subgraphs (communities) in a graph via random walks. The idea is that short random walks tend to stay in the same community.
• *infomap.community* [Rosvall and Bergstrom, 2008]: Find community struc- ture that minimizes the expected description length of a random walker tra jectory.



# Plot of results for a Network

```{r}
df <- read.csv("ER_net_df.csv")
  

df[,-c(1,ncol(df)-1,ncol(df))] %>% pivot_longer(-algorithm, names_to = "Var", values_to = "val") %>%
  ggplot(aes(x=Var,y=val,fill=algorithm)) +
    geom_bar(stat="identity",position="dodge") +
    scale_fill_discrete(name="algorithm") +
    xlab("Measure")+ylab("Value")

```


# Plot for different difficulty values

```{r}
defaultW <- getOption("warn")
options(warn = -1)
comm_sizes <- c(50,47,35,28)
ERp <- 0.4
est_clusters_ER <- list()
est_clusters_full <- list()
i <- 1
difficulties <- seq(10,200,5)
for (d in difficulties) {
  print(paste("ieration:",d))
  graph_ER <- merge_communities_ER(comm_sizes,ERp , difficulty = d)
  graph_full <- merge_communities_full(comm_sizes, difficulty = d)
  df_ER <- find_communities(graph_ER)
  df_full <- find_communities(graph_full)
  est_clusters_ER[[i]] <- df_ER$clusters
  est_clusters_full[[i]] <- df_full$clusters
  i <- i + 1
}
options(warn = defaultW)

results_ER <- list("edge.betweenness"=NULL,"fastgreedy"=NULL,"label.propagation"=NULL,"leading.eigenvector"=NULL,
            "multilevel"=NULL,"spinglass"=NULL,"walktrap"=NULL,"infomap"=NULL)
for (i in 1:length(algorithms)) {
  results_ER[[i]] <- as.numeric(lapply(est_clusters_ER, `[[`, i))
}

results_full <- list("edge.betweenness"=NULL,"fastgreedy"=NULL,"label.propagation"=NULL,"leading.eigenvector"=NULL,
            "multilevel"=NULL,"spinglass"=NULL,"walktrap"=NULL,"infomap"=NULL)
for (i in 1:length(algorithms)) {
  results_full[[i]] <- as.numeric(lapply(est_clusters_full, `[[`, i))
}

```

```{r}
save(results_ER,file="ER_difficulties_results_200.rda")
save(results_full, file="full_difficulties_results_200.rda")
load("ER_difficulties_results_200.rda")
load("full_difficulties_results_200.rda")

# estimated clusters

data.frame(results_ER) %>%  select(1:4) %>% mutate(difficulty=difficulties) %>%
  melt(id.vars="difficulty") %>%
  ggplot(aes( x=difficulty, y=value, colour=variable, group=variable )) + 
  geom_line(size=1) +
  geom_hline(y=mean,size=1) +
  geom_hline(yintercept=4, linetype="dashed", color = "red", size=0.5) +
  theme(text = element_text(size = 18),legend.position="bottom",legend.title = element_blank()) +
  ylab("estimated number of clusters") +
  guides(colour=guide_legend(nrow=2)) +
  ylim(c(2,8))


# estimated clusters

data.frame(results_ER) %>%  select(5:8) %>% mutate(difficulty=difficulties) %>%
  melt(id.vars="difficulty") %>%
  ggplot(aes( x=difficulty, y=value, colour=variable, group=variable )) + 
  geom_line(size=1) +
  geom_hline(yintercept=4, linetype="dashed", 
                color = "red", size=0.5) +
  theme(text = element_text(size = 18),legend.position="bottom",legend.title = element_blank()) +
  theme(legend.text=element_text(size=18)) +
  ylab("estimated number of clusters") +
  ylim(c(2,8))

```


# plot best configuration

```{r}
graph <- ER_net
graph <- as.undirected(graph, mode='collapse')
graph <- simplify(graph)
vertex_attr(graph) <- list(name=V(graph))
communities <- fastgreedy.community(graph)

plot(communities,graph)

```


# Plot timing

```{r}
nets <- list("macaque_net"=macaque_net,"Hospital_net"=rfid_net,
             "full_net"=full_net,"ER_net"=ER_net)


timings <- list()
for (i in 1:length(nets)) {
  print(paste("iteration:",i))
  net <- nets[[i]]
  net_name <- names(nets[i])
  df <- find_communities(net)
  timings[[i]] <- as.numeric(df$time)
  i <- i + 1
}

df_time <- data.frame(do.call(rbind,timings))
colnames(df_time) <- algorithms
df_time$network <- names(nets)

# plot

df_time %>% 
  melt(id.vars="network") %>% 
  ggplot(aes(fill=variable, y=value, x=network)) + 
    geom_bar(position="fill", stat="identity") +
  theme(text = element_text(size = 15)) +
  ylab("Relative elapsed time")

```









